---
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(data.table)
library(sf)
library(hrbrthemes)
library(ggthemes)
library(ggiraph)
library(ggimage)


# sorties
grid.cpt_flw_CLUB <- fread(  "./data_sorties/grid.cpt_flw_CLUB.csv") %>% filter(nb > 0)
grid.cpt_flw_DIST <- fread( "./data_sorties/grid.cpt_flw_DIST.csv")
fr_grid.ctr <- fread( "./data_sorties/fr_grid.ctr.csv")
ref.club <- fread( "./data_sorties/ref.club.csv")
dep.s <- st_read( "./data_sorties/dep.shp") 
cptOK_PAYS_flw_CLUB <- fread( "./data_sorties/cptOK_PAYS_flw_CLUB.csv")
cpt_flw_CLUB <- fread( "./data_sorties/cpt_flw_CLUB.csv")
comm.grid.liste.communes <- fread( "./data_sorties/comm.grid.liste.communes.csv") %>% select(id, NOM_COMM)



# fonction pour gérer accents
conv_accents <- function(x) {
  x <- gsub(pattern = "è", replacement = "&egrave;", x = x)
  x <- gsub(pattern = "é", replacement = "&eacute;", x = x)
  x <- gsub(pattern = "ê", replacement = "&ecirc;", x = x)
  x <- gsub(pattern = "ë", replacement = "&euml;", x = x)
  x <- gsub(pattern = "î", replacement = "&icirc;", x = x)
  x <- gsub(pattern = "ï", replacement = "&iuml;", x = x)
  x <- gsub(pattern = "û", replacement = "&ucirc;", x = x)
  x <- gsub(pattern = "ü", replacement = "&uuml;", x = x)
  x <- gsub(pattern = "ô", replacement = "&ocirc;", x = x)
  x <- gsub(pattern = "à", replacement = "&agrave;", x = x)
  x <- gsub(pattern = "â", replacement = "&acirc;", x = x)
  x <- gsub(pattern = "ç", replacement = "&ccedil;", x = x)
  
  x <- gsub(pattern = "è", replacement = "&Egrave;", x = x)
  x <- gsub(pattern = "é", replacement = "&Eacute;", x = x)
  x <- gsub(pattern = "ê", replacement = "&Ecirc;", x = x)
  x <- gsub(pattern = "ë", replacement = "&Euml;", x = x)
  x <- gsub(pattern = "î", replacement = "&Icirc;", x = x)
  x <- gsub(pattern = "ï", replacement = "&Iuml;", x = x)
  x <- gsub(pattern = "û", replacement = "&Ucirc;", x = x)
  x <- gsub(pattern = "ü", replacement = "&Uuml;", x = x)
  x <- gsub(pattern = "ô", replacement = "&Ocirc;", x = x)
  x <- gsub(pattern = "à", replacement = "&Agrave;", x = x)
  x <- gsub(pattern = "â", replacement = "&Acirc;", x = x)
  x <- gsub(pattern = "ç", replacement = "&Ccedil;", x = x)
  x <- gsub(pattern = "'", replacement = "&apos;", x = x)
  
  return(x)
}

```




```{r calculs, include=FALSE}

#unification stats  
grid.cpt_flw_CLUB.pct <- grid.cpt_flw_CLUB %>%
  left_join(grid.cpt_flw_DIST %>%
              as.data.frame() %>%
              select(id, nb_tot = nb), by = "id") %>%
  ungroup() %>%
  mutate(pct.CLUB = nb /  nb_tot) %>%
  left_join(fr_grid.ctr %>%
              as.data.frame() %>%
              select(id, x_ctr, y_ctr), by = "id") %>%
  arrange(nb)
  
# club max flw par carreau GRID
grid.cpt_flw_CLUB.pct.max <- grid.cpt_flw_CLUB %>%
  ungroup() %>%
  group_by(id) %>%
  filter(nb == max(nb)) %>%
  left_join(fr_grid.ctr %>%
              as.data.frame() %>%
              select(id, x_ctr, y_ctr), by = "id") %>%
  arrange(initiales_club) %>%
  left_join(ref.club %>%
              select(initiales_club, col_club),
            by = "initiales_club") %>%
  filter(!is.na(initiales_club))

# club #2 max flw par carreau GRID
grid.cpt_flw_CLUB.pct.max.2 <- grid.cpt_flw_CLUB %>%
  ungroup() %>%
  arrange(desc(nb)) %>%
  group_by(id) %>%
  slice(2:2) %>%
  left_join(fr_grid.ctr %>%
              as.data.frame() %>%
              select(id, x_ctr, y_ctr), by = "id") %>%
  arrange(initiales_club) %>%
  left_join(ref.club %>%
              select(initiales_club, col_club),
            by = "initiales_club") %>%
  filter(!is.na(initiales_club))


```

 
```{r carte_fans_clubs_giraphe_n1,echo=F, message=F, warning=F ,fig.height=5,fig.width=5, include=TRUE}


```{r dropdown_carte_densite_clubs_ggi_CV,echo=F, message=F, warning=F ,fig.height=1,fig.width=3}

library(bsselectR)

clubs_plots <- paste0(list.files("./dropdown_CV_html", pattern ="\\.html$",full.names = TRUE))
names(clubs_plots) <- str_replace_all(clubs_plots, 
                                      c("\\.html" = "", 
                                        "./dropdown_CV_html/" = ""))

bsselect(clubs_plots,
         frame_height = "700",
         frame_width = "80%", 
         header = FALSE,
         align_right = TRUE,
         width = 8,
         height = 4,
         box_width = "fit",
         #style = "btn-info",
         type = "iframe", selected = "Stade Rennais FC (SRFC)", 
         live_search = TRUE, show_tick = TRUE)


```


